---
title: "Lab 01 - Hello R"
author: "Haley Lam"
date: "1/15/2025"
output: 
  html_document: 
    theme: cosmo
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
data("datasaurus_dozen")
```

## Exercises

### Exercise 1

```{r}
data("datasaurus_dozen")

datasaurus_dozen %>%
  count(dataset) %>%
  print()
```

There are 3 columns (dataset, x, y) and 1846 observations

When doing count(dataset), it shows there are 13 datasets and 142 observations per dataset.

### Exercise 2

First, let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Next, let's calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
The points have no correlation. It's a dinosaur!


### Exercise 3

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
         geom_point()
```

A star with very scattered points! Now let's compute the meaningless correlation.

```{r cor-star}
star_data %>% 
  summarize(r = cor(x,y))
```
There was also little to no correlation between x and y, just like the dino.

### Exercise 4

Now time for a circle!

```{r}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

```{r}
circle_data %>% 
  summarize(r = cor(x,y))

```
There's also no correlation! (why are they all -0.06?)

### Exercise 5

Final exercise:
```{r fig.height=6, fig.width=5}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~dataset, ncol = 3) +
  theme(legend.position = "none")
```

```{r}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```

